Topics in Statistical Theory --- Example Sheet 1

### 2020-11-08 modern_statistical_methods/msm_ES2.tex
distribution theory is still difficult :((
lots of work done, lots of confusion going on

\begin{question}
	Consider the following algorithm for model selection when we have a response $Y \in \RR^n$ and a matrix of predictors $X \in \RR^{n \times p}$.
	\begin{enumerate}[(a)]
		\item First centre $Y$ and all the columns of $X$. Initiale the current model $M \subseteq \qty{1, \dotsc, p}$ to be $\emptyset$ and set the current residual $R$ to be $Y$. 
		\item Find the variable $k^*$ in $M^c$ most correlated with the current residual $R$. Set $M$ to be $M \cup \qty{k^*}$. Replace $R$ with the residual from regressing $R$ onto $X_{k^*}$. Further replac eeach variable in $M^c$ with the residual from regressing itself onto $X_{k^*}$.
		\item Continue the previous step unto $R = 0$. 
	\end{enumerate}
Show that this algorithm is equivalent to forward selection.

@@

\begin{solution}
	content...
\end{solution}

@@

\begin{proof}
	\begin{enumerate}[(a)]
		\item 
	\end{enumerate}
\end{proof}
\end{document}

>>>>

\begin{question}
	Consider the following algorithm for model selection when we have a response $Y \in \RR^n$ and a matrix of predictors $X \in \RR^{n \times p}$.
	\begin{enumerate}[(a)]
		\item First centre $Y$ and all the columns of $X$. Initiale the current model $M \subseteq \qty{1, \dotsc, p}$ to be $\emptyset$ and set the current residual $R$ to be $Y$. 
		\item Find the variable $k^*$ in $M^c$ most correlated with the current residual $R$. Set $M$ to be $M \cup \qty{k^*}$. Replace $R$ with the residual from regressing $R$ onto $X_{k^*}$. Further replace each variable in $M^c$ with the residual from regressing itself onto $X_{k^*}$.
		\item Continue the previous step unto $R = 0$. 
	\end{enumerate}
Show that this algorithm is equivalent to forward selection.

@@

\begin{solution}
We follow the hint and use induction on the iteration $m$ of the algorithm. For the base case, note that centering $Y$  is equivalent to fitting an intercept-only model. ???
\end{solution}

@@

\begin{proof}
	\begin{enumerate}[(a)]
		\item We have
		\begin{align*}
		\PP(\abs{W/d - 1} \geq t) &= \PP(W/d - 1 \geq t)+ \PP(W/d - 1 \leq -t) \\
		&= \PP(W\geq d(1+t)) + \PP(W \leq d(1 -t)). 
		\end{align*}

		Now we use Chernoff bounds: we have 
		\begin{align*}
		\PP(W \geq d(1+t))  &\leq \inf_{\alpha > 0} e^{-\alpha d(1 + t)} \EE[e^{\alpha W}] \leq \inf_{0 < \alpha < \frac12} e^{-\alpha dt} \qty(\frac{e^{-\alpha}}{\sqrt{1 - 2\alpha}})^d  \\
		&\leq \inf_{0 < \alpha < \frac14} e^{d(2\alpha^2 - \alpha t)} \overset\star=  e^{dt^2/8}, 
		\end{align*}
		where $\star$ is a consequence of plugging in the minimum $\alpha = t/4 \in (0, 1/4)$.

		Analogously, we have for $\alpha > 0$ that
		\begin{align*}
			\PP(W \leq d(1-t)) &\leq \inf_{\alpha > 0} e^{\alpha d(1-t)} \EE[e^{-\alpha W}] \leq \inf_{-\frac12 < \alpha < 0} e^{\alpha d t} \qty(\frac{e^{-\alpha}}{\sqrt{1 - 2\alpha}})^d \\
			&\leq \inf_{-\frac14 < \alpha < 0} e^{d(2\alpha^2 + \alpha t)} \overset\star= e^{dt^2/8},
		\end{align*}
	where $\star$ is now a consequence of plugging in the minimum $\alpha = -t/4 \in (-1/4, 0)$.

	Plugging what we found back into our original equation we obtain for $t \in (0, 1)$ indeed
	\[
	\PP(\abs{W/d - 1} \geq t) \leq 2e^{dt^2/8}. 
	\]

	\item We wish to show that $\norm{Au}^2/\norm{u}^2 \sim \chi_d^2$. For this, let $Z_1, \dotsc, Z_p$ be i.i.d.\ $N(0, 1)$ random variables, then 
	\[
	(Au)_i = \sum_{j=1}^p A_{ij} u_j \sim \sum_{j=1}^p u_j Z_j \sim N(0, \sum_i u_i^2) = N(0, \norm{u}_2^2). 
	\]
	Therfore, we have 
	\[
	\frac{\norm{Au}^2}{\norm{u^2}} = \frac{\sum_i (Au)_i^2}{\norm{u}^2} = \sum_i \qty(\frac{(Au)_i}{\norm{u}})^2 \sim \sum_i Z_i^2 \sim \chi_d^2. 
	\]
	Combining this with (a) proves the claim.

	\item We have
	\begin{align*}
			&\PP\qty(1 - t \leq \frac{\norm{w_i - w_j}_2^2}{\norm{u_i - u_j}_2^2} \leq 1 + t \text{ for all } i \neq j \in \qty{1, \dotsc, n})  \\
			&= \PP\qty(\abs{\frac{\norm{A (u_i - u_j)}^2}{d \norm{u_i - u_j}^2} - 1} \leq t \text{ for all } i \neq j \in \qty{1, \dotsc, n}) \\
			&= 1 - \PP\qty(\abs{\frac{\norm{A (u_i - u_j)}^2}{d \norm{u_i - u_j}^2} - 1} \geq t \text{ for some } i \neq j \in \qty{1, \dotsc, n}) \\
			&\overset\star\geq - \frac{n^2}{2} \cdot 2e^{-dt^2/8} \geq 1 - \eps, 
	\end{align*}
where $\star$ follows from the fact that there are $\frac{n(n-1)}{2} \leq \frac{n^2}{2}$ pairs $i \neq j$, and the last inequality follows from 
\[
e^{-dt^2/8} \leq e^{-2 \log(n/\sqrt\eps)} = \qty(\frac{n}{\sqrt\eps})^{-2} = \frac\eps{n^2}. 
\]
	\end{enumerate}
\end{proof}

\begin{mdframed}
	In the following questions, assume that $X$ has had its columns centred and scaled to have $\ell_2$-norm $\sqrt n$, and that $Y$ is also centred.
\end{mdframed}

\begin{question}
	Show that any two Lasso solutions when $\lambda > 0$ must have the same $\ell_1$-norm. 
\end{question}

\begin{proof}
	By proposition 21, $X\hat\beta_\lambda^L$ is unique, so if $\hat\beta$, $\hat\gamma$ are Lasso solutions then $X\hat\beta = X\hat\gamma$ so 
	\[
	Q_\lambda(\hat\beta) = \frac1{2n} \norm{Y - X\hat\beta}_2^2 + \lambda \norm{\hat\beta}_1 = \frac1{2n} \norm{Y - X\hat\beta}_2^2 + \lambda \norm{\hat\gamma}_1 = Q_\lambda(\hat\gamma), 
	\]
	which implies $\lambda \norm*{\hat\beta}_1 = \lambda \norm{\hat\gamma}_1$. For $\lambda > 0$ this shows $\norm{\hat\beta}_1 = \norm{\hat\gamma_1}$. 
\end{proof}

\begin{question}
	Carath\'eodory's Lemma states that if $S \subseteq \RR^{d'}$ is in a subspace of dimension $d$, any $v$ that is a convex combination of points in $S$ can be expressed as a convex combination of $d+1$ points from $S$.

	With this knowledge, show that for any value of $\lambda$, there is always a Lasso solution with no more than $n$ non-zero coefficients. 
\end{question}

\begin{proof}
	By the previous question, all Lasso solutions have the same norm $x$, so the set of Lasso solutions is given by
	\[
	\argmin_{\norm{\beta}_1 = x} \norm{Y - X\beta}_2^2.
	\]
	Let $\hat\beta$ be any fixed Lasso solution, then we find that the entire solution set can also be described as
	\[
	\qty{\hat\gamma \mid \norm{\gamma} = x, \hat\beta - \hat\gamma \in \Nul(X)}. 
	\]
	??
\end{proof}

\begin{question}
	Show that if $\lambda \geq \lambda_\Rm{max} \ceq \norm{X\T Y}_\infty / n$ then $\hat\beta_\lambda^L = 0$. 
\end{question}

\begin{proof}
	By the KKT conditions any lasso solution satisfies $\frac1n X\T (Y - X\hat\beta) = \frac1n X\T Y - \frac1n X\T X\hat\beta= \lambda \hat\nu$ for some $\nu$ with $\norm{\hat\nu}_\infty \leq 1$ and $\hat\nu_{\hat S_{\lambda}} = \sign(\hat\beta^L_{\lambda, \hat S_\lambda})$.

	Suppose $\lambda \geq \lambda_\Rm{max}$, and suppose also that $\hat\beta \neq 0$, so $\norm{\hat\nu}_\infty = 1$. Then we find
	\[
	\frac1n \norm{X\T (Y - X\hat\beta)}_\infty = \norm{\lambda\hat\nu} = \lambda  \geq \frac1n \norm{X\T Y}_\infty, 
	\]
	so 
	\[
	\norm{X\T Y - X\T X\hat\beta}_\infty \geq \norm{X\T Y}_\infty. 
	\]
	??
\end{proof}
\end{document}

### 2020-11-08 topics_statistical_theory/topics_ES1.tex
lots of work done, lots of confusion going on

\begin{solution}
	Note that $X/n$ is the average of $n$ i.i.d.\ random variables $Y_i \sim \Rm{Bern}(p)$, where $Y_i \in [0, 1]$ for all $i$.

	We start with Hoeffding's inequality. In this case, we have
	\[
	\PP(X/n - p \geq x) \leq \exp(-\frac{2n^2(1/2)^2}{n}) = \exp(- \frac n2),
	\]
	and this bound also holds as $p \to 0$.

	We continue with Bennett's inequality. We consider the random variables $Y_i - p$, which are bounded from above by $b = 1 - p$. Now Bennett's inequality tells us, with $\sigma_p^2 = \Var(Y_i - p) = p(1-p)$ that
	\begin{align*}
		\PP(X/n \geq x) &\leq \exp(- \frac{n}{(1-p)^2} h\qty(\frac{1-p}{2p(1-p)})) = \exp\qty(- \frac{n}{(1-p)^2} h\qty(\frac{1}{2p})).
	\end{align*}
We compute
\[
h\qty(\frac1{2p}) = (1 + \frac1{2p}) \log(1 + \frac1{2p}) - \frac1{2p} = \log(1 + \frac1{2p}) + \frac1{2p} \qty(\log(1 + \frac1{2p}) - 1) \overset{p \downarrow 0}\to +\infty. 
\]
Since $\frac{n}{(1-p)^2}$ is clearly bounded by $n$, we conclude that 
\[
\PP(X/n \geq x) \to e^{-\infty} = 0. 
\]

@@

We finish with Bernstein's inequality.  We have for $q \geq 3$ and $p \leq\frac12$ that 
\begin{align*}
	\EE[(Y_i - p)_+^q] &= p(1-p)^q = \sigma_p^2 (1-p)^{q-1} = (q! \sigma_p^2 (1-p)^{q-2}/2)\cdot (2(1-p)/q!) \\
	&\leq q!\sigma_p^2 ((1-p)/3)^{q-2}/2.
\end{align*}

Now Bernstein's inequality tells us that
\[
\PP(X/n \geq \frac12 \leq \exp\qty(- \frac{n(1/2)^2}{2(\sigma_p^2 + (1-p)/6)}) = \exp(- \frac{n}{8\sigma_p^2 + 4(1-p)/3}) \overset{p \to 0}{\to} \exp(-\frac{3n}{4}). \]

Of course, the true limit is 0 for any $n$, which is only given by Bennett's inequality. We also see that Hoeffding's inequality gives the worst result. 
\end{solution}

@@

\begin{solution}
	Note that $W_t = B_t - t B_1 = (1-t) (B_t - B_0) - t (B_1 - B_t)$. Now, since $(B_t - B_0)$ and $(B_1 - B_t)$ are independent with distributions $N(0, t)$ and $N(0, 1-t)$ distributions respectively, we find that 
	\[
	W_t \sim (1-t) N(0, t) + t N(0, 1 - t) = N\qty(0, \frac{t}{\sqrt{1 - t}}) + N\qty(0, \frac{1-t}{\sqrt t}) = N\qty(0, \frac{t}{\sqrt{1 - t}} + \frac{1-t}{\sqrt t}). 
	\]

@@

		\item Let $X_1, \dotsc, X_n \iid N(0, \sigma^2)$. Taking $K$ to be the $N(0, 1)$ density, show that the MISE of the kernel density estimate $\hat f_n$ with kernel $K$ and bandwidth $h$ can be expressed exactly as
		\[
		\MISE(\hat f_n) = (2\pi)^{-1/2} \qty{\frac1{nh} + (1 - \frac1n) \frac{1}{(h^2 + \sigma^2)^{1/2}} - \frac{2^{3/2}}{(h^2 + 2\sigma^2)^{1/2}} + \frac1\sigma}. 
		\]
	\end{enumerate}

@@

\begin{proof}
	\begin{enumerate}[(a)]
		\item We have
		\begin{align*}
			&\phantom{=\ }\frac{(x-\mu)^2}{\sigma^2} + \frac{(x - \mu')^2}{\sigma'^2} \\
			&= \frac{\sigma'^2(x - \mu)^2 + \sigma^2(x - \mu')^2}{\sigma^2\sigma'^2} \\
			&= \frac{(\sigma^2 + \sigma'^2)x^2 - 2 (\sigma'^2 \mu + \sigma^2 \mu')x + \sigma'^2 \mu^2 + \sigma^2\mu'^2}{\sigma^2 \sigma'^2} \\
			&=  \frac{(\sigma^2 + \sigma'^2)(x^2 - 2\mu^*x) + \sigma'^2 \mu^2 + \sigma^2\mu'^2}{\sigma^2 \sigma'^2} \\
			&= \frac{(\sigma^2 + \sigma'^2)(x^2 - 2\mu^* + \mu^{*2}) - (\sigma^2 + \sigma'^2)\mu^{*2} + \sigma'^2 \mu^2 + \sigma^2\mu'^2}{\sigma^2 \sigma'^2} \\
			&= \frac{(x - \mu^*)^2}{(\sigma\sigma'/(\sigma^2 + \sigma'^2)^{1/2})^2} + \frac{\sigma'^2 \mu + \sigma^2 \mu'^2 - (\sigma'^2\mu + \sigma^2\mu')^2/(\sigma^2 + \sigma'^2)}{\sigma^2\sigma'^2} \\
			&= \frac{(x - \mu^*)^2}{(\sigma\sigma'/(\sigma^2 + \sigma'^2)^{1/2})^2} + \frac{(\sigma^2 + \sigma'^2)(\sigma'^2\mu + \sigma^2\mu'^2) - (\sigma'^2\mu + \sigma^2\mu')^2}{\sigma^2 \sigma'^2(\sigma^2 + \sigma'^2)} \\
			&= \frac{(x - \mu^*)^2}{(\sigma\sigma'/(\sigma^2 + \sigma'^2)^{1/2})^2} + \frac{(\mu - \mu')^2}{\sigma^2 + \sigma'^2} \\
			&= \frac{(x - \mu^*)^2}{(\sigma\sigma'/(\sigma^2 + \sigma'^2)^{1/2})^2} + \frac{(\mu - \mu')^2}{((\sigma^2 + \sigma'^2)^{1/2})^2}, 
		\end{align*}
	which proves the claim. 
	\item Let $K = \phi_1$ and define $K_h(x) \ceq h^{-1} K(x/h)$ so $K_h = \phi_h$. Then recall from the lectures that
	\[
	\MISE(\hat f_n) = \frac1n \int_\RR \qty[(\phi_h^2 * \phi_\sigma)(x) - (\phi_h * \phi_\sigma)^2(x)] \dd{x} + \int_{-\infty}^\infty \qty[ (\phi_h * \phi_\sigma)(x) - \phi_\sigma]^2 \dd{x}
	\]
	\end{enumerate}
\end{proof}
\end{document}

>>>>

\begin{solution}
	Note that $X/n$ is the average of $n$ i.i.d.\ random variables $Y_i \sim \Rm{Bern}(p)$, where $Y_i \in [0, 1]$ for all $i$.  
	\begin{enumerate}
		\item

	We start with Hoeffding's inequality. In this case, we have
	\[
	\PP\qty(X/n - p \geq \frac12) \leq \exp(-\frac{2n^2(1/2)^2}{n}) = \exp(- \frac n2),
	\]
	and this bound also holds as $p \to 0$.

\item 	We continue with Bennett's inequality. We consider the mean-zero random variables $Y_i - p$, which are bounded from above by $b = 1 - p$. Now Bennett's inequality tells us that
	\begin{align*}
		\PP\qty(X/n \geq \frac12) &\leq \exp(- \frac{np(1-p)}{(1-p)^2} h\qty(\frac{1-p}{2p(1-p)})) = \exp\qty( -\frac{np}{1-p} \cdot  h\qty(\frac{1}{2p})).
	\end{align*}
We compute
\[
h\qty(\frac1{2p}) = \qty(1 + \frac1{2p}) \log(1 + \frac1{2p}) - \frac1{2p} = \log(1 + \frac1{2p}) + \frac1{2p} \qty(\log(1 + \frac1{2p}) - 1),
\]
and therefore
\[
\frac{np}{1-p} h\qty(\frac1{2p}) \geq  \frac{n}{2(1-p)} \qty(\log(1 + \frac1{2p}) - 1) \overset{p \to 0}\to \infty. 
\]
It follows that the Bennett upper bound converges to 0 as $p \to 0$.

@@

\item We finish with Bernstein's inequality.  We have for $q \geq 3$ that
\[
\frac{2(1-p)}{q!} \leq \frac2{q!} \leq 3^{2-q}, 
\]
and therefore we have
\begin{align*}
	\EE[(Y_i - p)_+^q] &= p(1-p)^q = \sigma_p^2 (1-p)^{q-1} = (q! \sigma_p^2 (1-p)^{q-2}/2)\cdot (2(1-p)/q!) \\
	&\leq q!\sigma_p^2 ((1-p)/3)^{q-2}/2,
\end{align*}
so $Y_i - p$ satisfies Bernstein's condition with $c = \frac{1-p}{3}$.
Now Bernstein's inequality tells us that
\[
\PP(X/n \geq \frac12 \leq \exp\qty(- \frac{n(1/2)^2}{2(\sigma_p^2 + (1-p)/6)}) = \exp(- \frac{n}{8\sigma_p^2 + 4(1-p)/3}) \overset{p \to 0}{\to} \exp(-\frac{3n}{4}). \]
	\end{enumerate}
Of course, the true limit is 0 for any $n$, which is only given by Bennett's inequality. We also see that Hoeffding's inequality gives the most loose bound.

\end{solution}

@@

\begin{solution}
	Note that $W_t = B_t - t B_1 = (1-t) (B_t - B_0) - t (B_1 - B_t)$. Now, since $(B_t - B_0)$ and $(B_1 - B_t)$ are independent with distributions $N(0, t)$ and $N(0, 1-t)$ distributions respectively, we find that 
	\[
	W_t \sim (1-t) N(0, t) + t N(0, 1 - t) = N\qty(0, t(1-t)^2) + N\qty(0, t^2(1-t)) = N\qty(0, t(1-t)). 
	\]

@@

		\item Let $X_1, \dotsc, X_n \iid N(0, \sigma^2)$. Taking $K$ to be the $N(0, 1)$ density, show that the MISE of the kernel density estimate $\hat f_n$ with kernel $K$ and bandwidth $h$ can be expressed exactly as
		\[
		\MISE(\hat f_n) = \frac1{2\pi^{1/2}} \qty{\frac1{nh} + (1 - \frac1n) \frac{1}{(h^2 + \sigma^2)^{1/2}} - \frac{2^{3/2}}{(h^2 + 2\sigma^2)^{1/2}} + \frac1\sigma}. 
		\]
	\end{enumerate}

@@

\begin{proof}
	\begin{enumerate}[(a)]
		\item We have
		\begin{align*}
			&\phantom{=\ }\frac{(x-\mu)^2}{\sigma^2} + \frac{(x - \mu')^2}{\sigma'^2} \\
			&= \frac{\sigma'^2(x - \mu)^2 + \sigma^2(x - \mu')^2}{\sigma^2\sigma'^2} \\
			&= \frac{(\sigma^2 + \sigma'^2)x^2 - 2 (\sigma'^2 \mu + \sigma^2 \mu')x + \sigma'^2 \mu^2 + \sigma^2\mu'^2}{\sigma^2 \sigma'^2} \\
			&=  \frac{(\sigma^2 + \sigma'^2)(x^2 - 2\mu^*x) + \sigma'^2 \mu^2 + \sigma^2\mu'^2}{\sigma^2 \sigma'^2} \\
			&= \frac{(\sigma^2 + \sigma'^2)(x^2 - 2\mu^* + \mu^{*2}) - (\sigma^2 + \sigma'^2)\mu^{*2} + \sigma'^2 \mu^2 + \sigma^2\mu'^2}{\sigma^2 \sigma'^2} \\
			&= \frac{(x - \mu^*)^2}{(\sigma\sigma'/(\sigma^2 + \sigma'^2)^{1/2})^2} + \frac{\sigma'^2 \mu + \sigma^2 \mu'^2 - (\sigma'^2\mu + \sigma^2\mu')^2/(\sigma^2 + \sigma'^2)}{\sigma^2\sigma'^2} \\
			&= \frac{(x - \mu^*)^2}{(\sigma\sigma'/(\sigma^2 + \sigma'^2)^{1/2})^2} + \frac{(\sigma^2 + \sigma'^2)(\sigma'^2\mu + \sigma^2\mu'^2) - (\sigma'^2\mu + \sigma^2\mu')^2}{\sigma^2 \sigma'^2(\sigma^2 + \sigma'^2)} \\
			&= \frac{(x - \mu^*)^2}{(\sigma\sigma'/(\sigma^2 + \sigma'^2)^{1/2})^2} + \frac{(\mu - \mu')^2}{\sigma^2 + \sigma'^2} \\
			&= \frac{(x - \mu^*)^2}{(\sigma\sigma'/(\sigma^2 + \sigma'^2)^{1/2})^2} + \frac{(\mu - \mu')^2}{((\sigma^2 + \sigma'^2)^{1/2})^2}, 
		\end{align*}
	which proves the claim. 
	\item Let $K = \phi_1$ and define $K_h(x) \ceq h^{-1} K(x/h)$ so $K_h = \phi_h$. Then recall from the lectures that
	\[
	\MISE(\hat f_n) = \frac1n \int_\RR \qty[(\phi_h^2 * \phi_\sigma)(x) - (\phi_h * \phi_\sigma)^2(x)] \dd{x} + \int_{-\infty}^\infty \qty[ (\phi_h * \phi_\sigma)(x) - \phi_\sigma(x)]^2 \dd{x}
	\]

	We will use the previous exercise to compute all these terms. 
	We have in general 
	\begin{align}
		(\phi_h * \phi_\sigma)(x) &= \int_\RR \phi_h(x-z) \phi_\sigma(z) \dd{z}\nonumber \\
		&= \int_\RR \phi_\sigma(z) \phi_h(z-x) \dd{z} \nonumber\\
		&= \phi_{(\sigma^2 + h^2)^{1/2}}(x) \int_\RR \phi_\xi(z - \mu^*) \dd{z} \nonumber\\
		&= \phi_{(\sigma^2 + h^2)^{1/2}}(x) \label{eq:normal_convolve}. 
	\end{align}

	We also have
	\begin{equation} \label{eq:normal_squared}
	\phi_\sigma^2(x-\mu) = \phi_{\sigma/\sqrt 2}(x - \mu) \phi_{\sqrt 2 \sigma}(0) = \frac{1}{2 \sigma \sqrt\pi} \phi_{\sigma/\sqrt 2}(x - \mu). 
	\end{equation}

	Combining \cref{eq:normal_convolve,eq:normal_squared} we get 
	\begin{align*}
		(\phi_h^2 * \phi_\sigma)(x) &= \int_\RR \phi_h^2(x-z) \phi_\sigma(z) \dd{z} \\
		%&= \phi_{\sqrt 2 h}(0) \int_\RR \phi_{h/\sqrt 2}(x - z)  \phi_\sigma(z) \dd{z} \\
		&= \frac{1}{2h \sqrt \pi } \int_\RR \phi_{h/\sqrt 2}(x - z) \phi_{\sigma}(z)  \dd{z} \\
		&= \frac{1}{2h\sqrt \pi} (\phi_{h/\sqrt 2} * \phi_\sigma)(x) \\
		&= \frac{1}{2h \sqrt\pi} \phi_{(\sigma^2 + h^2/2)^{1/2}}(x)
%		&= \frac{1}{2h \sqrt \pi} \phi_{\xi'}(x) \int_\RR \phi_\xi(z - \mu^*) \dd{z} \\
%		&= \frac{1}{2h\sqrt\pi} \phi_{\xi'}(x),
	%\\ &= \frac{1}{2\sqrt{\pi h}} \int_\RR \phi_{\xi}(z - \mu^*) \phi_{(\sigma^2 + h^2/2)^{1/2}}(x-z)
	\end{align*}
	\end{enumerate}

	We also get
	\[
	(\phi_h * \phi_\sigma)^2(x) = \phi_{(\sigma^2 + h^2)^{1/2}}^2(x) = \frac{1}{2 (\sigma^2 + h^2)^{1/2} \sqrt\pi} \phi_{(\sigma^2 + h^2)^{1/2}/\sqrt 2}(x).
	\]

	Finally, we have
	\begin{align*}
		((\phi_h * \phi_\sigma)(x) - \phi_\sigma(x))^2 &= (\phi_h * \phi_\sigma)^2(x) - 2 (\phi_h * \phi_\sigma)(x) \phi_\sigma(x) + \phi_\sigma^2(x).
	\end{align*}
	The first term we already computed, the third term is $\frac{1}{2\sigma\sqrt\pi} \phi_{\sigma/\sqrt 2}(x)$, so we only need to compute
	\begin{align*}
		(\phi_h * \phi_\sigma)(x) \phi_\sigma(x) &= \phi_{(\sigma^2 + h^2)^{1/2}}(x) \phi_\sigma(x) = \phi_{\xi}(x) \phi_{(2\sigma^2 + h^2)^{1/2}}(0) = \frac{1}{\sqrt{2\pi} (2\sigma^2 + h^2)^{1/2}} \phi_\xi(x),
	\end{align*}
where $\xi$ is an irrelevant constant.

Combining all these terms and using that $\phi_\sigma(x-\mu)$ integrates to 1 for any $\mu, \sigma$, we get
\begin{align*}
	\MISE \hat f_n &= \frac1n \qty(\frac1{2h\sqrt\pi} - \frac{1}{2(\sigma^2 + h^2)^{1/2}\sqrt\pi}) + \frac{1}{2(\sigma^2 + h^2)^{1/2}\sqrt\pi} - \frac{\sqrt 2}{\sqrt\pi (2\sigma^2 + h^2)^{1/2}} + \frac{1}{2\sigma\sqrt\pi} \\
	&= \frac{1}{2\sqrt\pi} \qty(\frac{1}{nh} + (1 - \frac1n) \frac{1}{(\sigma^2 + h^2)^{1/2}} - \frac{2^{3/2}}{(2\sigma^2 + h^2)^{1/2}} + \frac1\sigma). 
\end{align*}
\end{proof}

\begin{question}
	Use the expression from 10(b) to derive an upper bound of the form $\MISE \hat f_n \leq C_1/(nh) + C_2^2 h^4$ (where you should specify $C_1, C_2$). Show that $\phi_\sigma \in \FF_\Nn(2, L)$ with $L^2 = 3/(8 \pi^{1/2} \sigma^5)$, and hence compare the bound from the first part of this question with that obtained from the general theory from lectures. 
\end{question}

\begin{solution}
	We have 
	\[
	\qty(1 - \frac1n) \frac{1}{(\sigma^2 + h^2)^{1/2}} - \frac{2^{3/2}}{(2\sigma^2 + h^2)^{1/2}} \leq \frac{1}{(\sigma^2 + h^2)^{1/2}}  - \frac{2}{(\sigma^2 + h^2/2)^{1/2}} < 0,
	\]
%	and therefore
%	\[
%	\MISE \hat f_n < \frac{1}{2\sqrt\pi} \qty(\frac1{nh} + \frac1\sigma). 
%	\]
	I do not know how to obtain an upper bound of the form $C_1/(nh) + C_2^2 h_4$ from this expression.

	To show that $\phi_\sigma \in \FF_\Nn(2, L)$,  we must show that $\phi_\sigma \in \FF_\Nn(2, L)$. By question 9, it suffices to show that $\norm{\phi''_\sigma}_{L^2}^2 \leq L^2$. 
	A simple computation gives
	\[
	\phi_\sigma''(x) = \frac{1}{\sqrt{2\pi} \sigma^5} \qty(x^2 - \sigma^2) \exp(-\frac{x^2}{2\sigma^2}) \leq \frac1{\sqrt{2\pi} \sigma^5} x^2 \exp(-\frac{x^2}{2\sigma^2})
	\]
	so
	\begin{align*}
	\norm{\phi_\sigma''}_{L^2}^2 &\leq \frac{1}{2\pi\sigma^{10}} \int_\RR x^4 \exp(-\frac{x^2}{\sigma^2}) \dd{x} \overset\star= \frac{1}{2\pi \sigma^{10}} \cdot \frac34 \sqrt{\pi} \sigma^5 = \frac{3}{8 \sqrt\pi \sigma^5} = L^2, 
	\end{align*}
where $\star$ can be computed using the fact that the integral is, up to scaling, the fourth moment of $N(0, \sqrt2\sigma)$ distribution.

Note that for $K = \phi_1$, we have 
\[
R(K) = \int_{-\infty}^\infty \phi_1^2(x) \dd{x} = \frac1{2\sqrt\pi}, 
\]
while
\[
\mu_2^2(K)=  \int_{-\infty}^\infty x^2 \phi_1(x) \dd{x} = 1.
\]

Plugging all the above into theorem 27 shows that 
\[
\MISE(\hat f_n) \leq \frac{1}{2\sqrt\pi} \frac1{nh} + \frac{3}{8\sqrt\pi \sigma^5} h^4.
\]
\end{solution}

\begin{question}
	Let $f$ be a bounded density that is twice differentiable at $x \in \RR$ and satisfies $R(f'') < \infty$. Let $h = h_n$ be deterministic, with $h \to 0$ and $nh \to \infty$ as $n\to\infty$, and let $K$ be a second-order kernel with $\max\qty{R(K), \mu_2(K)} < \infty$. Show that the KDE $\hat f_n \equiv \hat f_{n, h, K}$ satisfies
	\[
	\MSE (\hat f_n(x)) = \frac1{nh} R(K) f(x) + \frac14 \mu_2^2(K) f''(x)^2 h^4 + o\qty(\frac1{nh} + h^4)
	\]
	as $n\to\infty$. 
\end{question}

\begin{proof}
	As in the proof of proposition 19, we have
	\[
	\Var \hat f_n(x) %= \frac1{nh} \int_{-\infty}^\infty K^2(u) f(x - uh) \dd{u}
	\]
%	Now we use a Taylor expansion 
%	\[
%	f(x - uh) = f(x) - f'(x) uh + \frac{(uh)^2}{2} \int_0^1 f''(x - \tau uh) (1 - \tau) \dd{\tau},
%	\]
%	and we obtain
%	\[
%	\Var \hat f_n(x) = \frac1{nh} \qty(f(x) \int_{-\infty}^\infty K^2(u) \dd{u})
%	\]
\end{proof}
\end{document}
